CMPSubset

### 2021-08-19 CMP/CMPSubset.Rmd
Add dim25 biomark targets

# Total var 85%
## Neighborhood and umap
set total.var <- 85%
```{r}
tot.var <- percent.variance(cmp.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 85))

@@

@@

>>>>

# Total var 85%
## Neighborhood and umap
set total.var <- 85%
```{r}
tot.var <- percent.variance(cmp.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 85))
```

```{r}
cmp.object <- FindNeighbors(cmp.object, dims = 1:ndims)
cmp.object <- FindClusters(cmp.object, resolution = 0.5)
cmp.object <- RunUMAP(cmp.object, dims = 1: ndims)
```
Plot UMAP

@@

```{r}
for (meta.col in colnames(cmp.object@meta.data)){
	if(grepl(pattern = ("RNA_snn_res"), x = meta.col)==TRUE){
		plot.title <- paste0(projectName, "dim", ndims, "res", gsub("RNA_snn_res", "", meta.col))
		myplot <- DimPlot(cmp.object, 
											group.by = meta.col,
											reduction = "umap", 
											cols = color.palette
											) + 
			ggtitle(plot.title)
		plot(myplot)
		png(filename = paste0(plot.title, ".png"), height = 800, width = 800)
		plot(DimPlot(cmp.object, 
											group.by = meta.col,
											reduction = "umap", 
											cols = color.palette, 
											pt.size = 1.5
											) + 
			ggtitle(plot.title)
			)
		dev.off()
	}
}
```

@@

Here's the list of genes, plus some controls
```{r}
res1.biomark.genes <- c("Aif1",
"Aqp1",
"Birc5",
"Ccl3",
"Ccr2",
"Cd74",
"Cdc20",
"Cenpf",
"Cst3",
"Ctsh",
"Dntt",
"Elane",
"Ermap",
"F13a1",
"Fcer1g",
"Gm15915",
"Gm17590",
"H2-Aa",
"H2-Eb1",
"H2afx",
"H2afy",
"Hist1h2ac",
"Hmgb2",
"Hp",
"Ighm",
"Irf8",
"Lgals3",
"Lmo4",
"Ms4a2",
"Mt1",
"Plac8",
"Prtn3",
"Rap1b",
"Rgs1",
"Vwf",
"Wfdc17",
"Csrp3",
"Hist1h2ae",
"Ifitm1",
"Lgals1",
"Tmsb4x",
"Arl6ip1",
"Car2",
"Ccl9",
"Ccnb2",
"Cd9",
"Cenpa",
"Cpa3",
"Fos",
"Hist1h2ap",
"Ly6c2",
"Mpo",
"Pclaf",
"Slpi",
"Top2a",
"Ube2c",
"Ly86",
"Hist1h2bc",
"Pf4",
"Apoe",
"Ctsg",
"Car1",
"Hmmr", 
"Gapdh", 
"B2m", 
"Actb", 
"Hprt1",
"Gusb")
```

make vln plots per cluster
```{r}
for(gene in res1.biomark.genes){
	plot.title <- paste0(projectName, "dim", ndims, "res1_", gene)
	myplot<- VlnPlot(cmp.object, features = gene, pt.size = 0.01) + ggtitle(plot.title)
	png(filename = paste0(plot.title, ".png"), height = 800, width = 1600)
	plot(myplot)
	dev.off()

## Res 1.5
